Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-03-27 paper/paper-nature_format.qmd
minor edits

---
title: "Digitization of the Australian Parliamentary Debates, 1998-2022"
number-sections: true
format: 
  pdf:
    keep-tex: true
bibliography: references.bib
editor: visual
date: "now"
date-format: long
author:
  - Lindsay Katz^[University of Toronto, lindsay.katz@mail.utoronto.ca]
  - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca]
abstract: "Public knowledge of what is said in parliament is a key tenet of democracy, and a critical resource for political science research. In Australia, following the British tradition, the written record of what is said in parliament is known as Hansard. While the Australian Hansard has always been publicly available, it has been difficult to use it for the purpose of large-scale macro and micro-level text analysis because it has not been available as a dataset of sufficient quality. Following the lead of the Linked Parliamentary Data project which achieved this for Canada, we provide a new, comprehensive, high-quality database that captures all proceedings of the Australian parliamentary debates from 1998 to the present using Hansard. The database is publicly available and can be readily linked to other datasets such as election results. The creation and accessibility of this database will enable the exploration of questions that are not currently possible to explore, serving as a valuable resource for both researchers and policymakers."
---

@@

The official written record of parliamentary debates, formally known as Hansard, plays a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions. Originating in the British parliament, the production of Hansard became tradition in a number of Commonwealth countries such as Canada, the United Kingdom, and Australia [@vice2017history]. Given the content and magnitude of these records, they have significance, particularly in the context of political science research. In the case of Canada, a team of researchers at the University of Toronto have digitized Hansard from 1901 to 2019, an endeavour called the Linked Parliamentary Data (LiPaD) project [@lipad]. Having a digitized version of Hansard enables researchers to perform advanced analyses on these records using text analysis tools and statistical modelling. Following the lead of the LiPaD project, in this paper we introduce a novel database for the Australian Hansard. This is composed of individual datasets for each sitting day in the House of Representatives from 1998 to 2022, containing details on everything said in parliament in a form which can be readily used by researchers. With the development of tools for large-scale text analysis, this database will serve as a valuable resource for efficiently studying and exploring political behaviour in Australia over time.

The House of Representatives performs a number of crucial governmental functions, such as creating new laws and overseeing government expenditure [@australia2018house, ch. 1]. The House operates under a parallel chamber setup, meaning there are two debate venues where proceedings take place: the Chamber, and the Federation Chamber. Sittings of the House follow a predefined order of business, regulated by procedural rules called standing orders [@australia2018house, ch. 8]. A typical sitting day in the Chamber has a number of scheduled proceedings including debates on government business, 90 second member statements, and Question Time [@australia2018house, ch. 8]. The Federation Chamber was created in 1994 as a subordinate debate venue of the Chamber. This allows for better time management of House business as its proceedings occur simultaneously with those of the Chamber [@australia2018house, ch. 21]. Sittings in the Federation Chamber are quite different to those of the Chamber in terms of their order of business and scope of discussion. Business matters discussed in the Federation Chamber are limited largely to intermediate stages of bill development, and the business of private Members [@australia2018house, ch. 21]. It is the recording and compilation of all of these proceedings on which Hansard is based, and it is essentially, but not entirely, verbatim.

A week or so after each sitting day, a transcript is available for download from the official Parliament of Australia website in both static PDF and extensible markup language (XML) form. The PDF is the official release, which is converted to typed text using Optical Character Recognition (OCR) technology [@sherratt]. This conversion allows for the production of the XML formatted transcript, though these are not always perfect conversions and are particularly flawed in the early decades of Hansard [@sherratt]. The PDF imposes formatting designed for humans to read with ease, whereas XML is designed for consistency and machine legibility. The nature of XML enables us to more easily use code to manipulate these records at scale, motivating our choice to develop our database solely using the XML formatted files. In cases where we were unsure on how to proceed with processing the XML, we defer first to the PDF, and then to the video recording of the proceeding if available.

At present, the Hansard format that is available on the Parliament of Australia website is not accessible for large scale analysis. To this point, various researchers have had to create their own databases in an attempt to produce usable, complete data based on content from the Australian Parliament website. For instance, @sherratt created an online, easy to read database of Hansard from 1901 to 1980 using the XML files. These data can be navigated by year, parliament, people, and bills [@sherratt]. In an effort to make the Australian Parliamentary Handbook more accessible, @Leslie_2021_HoR_Aus has released an `R` package which includes data on all Members of the Australian House of Representatives from 1945 to 2019. Further, @auspol created the `AustralianPoliticians` `R` package, which contains a number of datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021.

A number of papers exist which utilize components of Australian Hansard to explore various research topics. For example, @salisbury2011 used online Hansard records to investigate the occurrences of unparliamentary comments by members of the House, where The Speaker tells that member to withdraw their remark. @rasiah2010framework worked with Question Time data from Hansard transcripts during February and March of 2003, to investigate resistance of politicians in answering questions about Iraq. In their work, @fraussen2018 use Hansard to quantify political prominence by investigating strategic mentions of interest groups by elected officials. Finally, the work of @alexander2021 offers a dataset of the Australian Hansard, along with an analysis of the effect of elections and changes in Prime Ministers upon topics mentioned in parliament. @alexander2021 created this database with the static PDF versions of Hansard, using OCR to digitize these files into text which is suitable for analysis. This means there are considerable digitization errors especially in the first half of the dataset.

@@

>          <hansard>
>            1. <session.header>
>            2. <chamber.xscript>
>               a)  <business.start>
>               b)  <debate>
>                   i.  <debateinfo>
>                   ii. <debate.text>
>                   iii. <speech>
>                   iv. <subdebate.1>
>                       (1) <subdebateinfo>
>                       (2) <subdebate.text>
>                       (3) <speech>
>                       (4) <subdebate.2>
>                           (a) <subdebateinfo>
>                           (b) <subdebate.text>
>                           (c) <speech>
>           3. <fedchamb.xscript>
>           4. <answers.to.questions>
>               a)  <question>
>               b)  <answer>

The outer-most node, also known as the parent node, is denoted `<hansard>` and serves as a container for the entire document. This parent node may have up to four child-nodes, where the first child-node contains details on the specific sitting day. Next, `<chamber.xscript>` contains all proceedings of the Chamber, `<fedchamb.xscript>` contains all proceedings of the Federation Chamber, and `<answers.to.questions>` contains Question Time proceedings. Note that the Federation Chamber does not meet on every sitting day, so this child element is not present in every XML file. The use of separate child nodes allows for the distinction of proceedings of the Chamber and Federation Chamber. The structure of the `<chamber.xscript>` and `<fedchamb.xscript>` nodes are generally the same, where the proceeding begins with a business start which is followed by a series of debates. Debate nodes can contain a sub-debate 1 child-node which has a sub-debate 2 child-node nested within it. That said, sometimes sub-debate 2 is not nested within sub-debate 1. Each of these three elements (i.e. `<debate>`, `<subdebate.1>`, and `<subdebate.2>`) as well as their respective sub-elements contain important information on the topic of discussion, who is speaking, and what is being said. The `<speech>` node within each one contains the bulk of the text associated with that debate or sub-debate. A typical `<speech>` node begins with a `<talk.start>` sub-node, providing information on the speaker and the time of their first statement. Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate settings --- they are often composed of a series of interjections and continuations. These statements are categorized under different sub-nodes depending on their nature, such as `<interjection>` or `<continuation>`. The final key component of Hansard is Question Time, in which questions and answers are classified as unique elements. More detail on the purpose and processing of Question Time will follow in @sec-qa.

@@

**does this feel a bit repetitive? do you think it's worth keeping?**

![Snapshot of beginning of XML file for Hansard on 25 February 2020](images/xml1.png){#fig-xml1}

@@

The next step was to further develop our script to produce tidy data sets containing each parsed element, where each statement is separated onto its own row with details about the speaker, and rows are placed in chronological order. This first involved correcting the variable classes and adding a number of indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or sub-debate 1 versus sub-debate 2. The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed. In other words, any interjections, comments made by The Speaker or Deputy Speaker and continuations within an individual speech were all parsed together as a single string. As such, the name, name ID, electorate and party details were only provided for the person whose turn it was to speak. Splitting up these speeches in a way which would be generalizable across sitting days required much thought and effort. @sec-interject will provide further details on the intricacies of this task.

Since we are looking at a wide time span of documents, there are expectedly a number of changes in the way they are formatted over time. These became apparent as we ran our script on XML files from earlier sitting days. Some changes are as subtle as a differently named child-node, while others are as extensive as a completely different nesting structure. Smaller changes were accounted for as we became aware of them, and embedded into the code in a way that would not cause issues for parsing more current Hansards with subtle differences in formatting. However, as mentioned, more significant changes in the XML structure of Hansard are what necessitated the development of separate scripts as we worked backwards in time. Further, while working backward in time, it became clear that not every sitting day contains every possible XML element. For example, some days did not have sub-debate 2 content, and some days did not have a Federation Chamber proceeding. To improve the generalizability of these scripts, if-else statements were embedded within the code wherever an error might arise due to a missing element. For example, the entire Federation Chamber block of code is wrapped in an if-else statement for each script, so that it only executes if what the code attempts to parse actually exists in the file.

@@

While the modifications needed to develop the second script were quite straightforward, this was not the case for our next script. The typical tree structure of Hansard XMLs spanning from 1998 to March 2011 has an important difference from that of XMLs released after March 2011, necessitating many changes to be made in our methodology. In XMLs after March 2011, which our first two scripts successfully parse, the first two child-nodes of `<speech>` are typically `<talk.start>`, and `<talk.text>`. The first child-node contains data on the person whose turn it is to speak, and the second contains the entire contents of that speech --- including all interjections, comments and continuations. After the `<talk.text>` element closes, there are typically a series of other child-nodes which provide a skeleton structure for how the speech proceedings went in chronological order. For example, if the speech began, was interrupted by one member, and then continued uninterrupted until the end, there would be one `<interjection>` node and one `<continuation>` node following the `<talk.text>` node. These would contain details on the person who made each statement such as their party and electorate.

@@

This was not isolated to just the beginning of speeches --- details on individuals interjecting or commenting during speeches were also captured this way. To separate statements out correctly, we collected all of these patterns using the `<talk.start>` node, and used them to split statements wherever one of these patterns was found. After separating statements, we were later able remove these patterns from the body of text. We also used this method of extracting and later removing unwanted patterns for other pieces of data which did not belong to the debate proceedings, such as sub-debate titles.

Once we finalized this new method of processing the data, we proceeded with data cleaning using the same general approach as in the first two scripts to produce the same structure of CSV output. We then worked backwards in time and modified the code as needed for generalizability. Throughout this process we found a number of transcription errors present in the XMLs from earlier years. We fixed these manually, deferring to the official release to ensure the correct information was filled in. Since there were a number of transcription errors specific to the 2000s, we chose to create a fourth script for parsing 1998 and 1999. This allowed us to remove all the code which was needed to resolve specific transcription errors of the 2000s, to avoid an overly long script and in turn improving computational efficiency. As such, our fourth script is essentially the same as the third, the only difference being that it has code specific to fixing transcription errors from 1998 and 1999.

@@

A key characteristic of the Australian parliament system is the ability for the executive government to be held accountable for their decisions. One core mechanism by which this is achieved is called Question Time. This is a period on each sitting day in the Chamber where members of the House can ask ministers two types of questions: questions in writing which are written in advance, or questions without notice which are asked verbally in the Chamber and are responded to in real time [@house2021]. Parsing the components of Question Time required a slightly different approach than that of the debate speech, because of its unique structure in the XML document. Questions without notice are included directly in the `"chamber.xscript"` child node, with sub-child nodes called `"question"` and `"answer"` to differentiate the two. Questions in writing, however, are embedded in their own child node called `"answers.to.questions"` at the end of the XML file.

To parse questions without notice and questions in writing in the first two scripts, we extracted all question and answer elements from the `"chamber.xscript"` and `"answers.to.questions"` child nodes. For the third and fourth scripts, our method of parsing the `"chamber.xscript"` speeches meant that all questions without notice content was already parsed in order. Similar to the rest of the speech content, we used those patterns of data preceding the text to separate questions and answers. Finally, since questions in writing exist in their own child node we were able to use the same parsing method for the third and fourth scripts as we did for the first and second scripts.

@@

As mentioned in @sec-diff, more recent years of Hansard XMLs contain a series of child-nodes which exist to capture the structure of interruptions in that speech. @fig-xml3 provides an example of this, where the speech was interrupted by a comment from The Deputy Speaker, and then the member continued their speech. Looking at the element names highlighted in blue, it is clear that these child-nodes do not contain the actual text for the interjection or continuation --- this text is embedded within the speech above it. However, as shown by the content highlighted in pink in @fig-xml3, we were able to extract useful details on the individual interjecting which we could use later on. Making use of this structure, we extracted names and information of all individuals that were categorized within the XML as interjections. We stored this as a dataframe called `"interject"`.[^1]

@@

We then created lists using both the `interject` and `main` dataframes to capture all the names of individuals who spoke that day. We added the names of all Members in a number of unique formats, due to the frequent variation in how names are transcribed in Hansard. When a Member interjects or continues a speech, the usual form of their name is a title followed by their first name or first initial and/or last name. There is also variation in the capitalization of these names.[^2] Another source of variation is in individuals with more than one first name, as sometimes only their first first name is written, while other times their entire first name is written. Additionally, some surnames have punctuation, and some surnames have specific capitalization such as "McCormack", where even in full capitalization, the first "c" remains lower case. This variation demands careful consideration when writing regular expression patterns to search for in the text. In these lists we also accounted for any general interjection statements transcribed that were not attributed to an individual, such as "An opposition member interjecting-".

[^2]: Sometimes when someones first name is included, only their last name is capitalized, while sometimes their full name is capitalized, or other times neither are capitalized.

Having these lists enabled us to extract the names of Members and their associated titles as they exist in the text, by searching for exact matches with regular expression patterns. We then used these extracted names to split all the speeches up, using a number of regular expressions with lookarounds. A lookaround can be added to a regular expression pattern to enhance the specificity of matches. These were used to ensure that the text was not being split in the wrong places, such as places where Members were simply being named in the statement of another Member.

@@

We then added an order variable to the dataset based on row number, to keep track of the order in which everything was said. The next step was to fill the name, name ID, electorate and party variables with the correct data for each row. We also wanted to add the gender and unique identifier for each individual as found in the `AustralianPoliticians` package. To do so, we created a lookup table, which contained the unique incomplete form in which the name was transcribed, and the corresponding full name, name ID, electorate, party, gender and unique ID for that individual. @fig-lookup provides an example of this. We used the main dataset from the `AustralianPoliticians` package in the creation of each lookup table [@auspol].

@@

Next, we merged our main dataframe with the lookup table to replace any incomplete names with their full names, and to fill in any gaps with available name ID, electorate, party, gender and unique ID information. Finally, we were able to add a flag for interjections. Grouping our data by the speech number, we defined an interjection as a statement made by anyone who is not The Speaker, The Deputy Speaker, or the Member whose turn it was to speak. @fig-interject provides an example of a Federation Chamber proceeding with interjections. Evidently, statements made by the original speaker Stuart Robert or by The Deputy Speaker Maria Vamvakinou are not flagged as interjections.

>>>>

---
title: "Digitization of the Australian Parliamentary Debates, 1998-2022"
number-sections: true
format: 
  pdf:
    keep-tex: true
bibliography: references.bib
editor: visual
date: "now"
date-format: long
author:
  - Lindsay Katz^[University of Toronto, lindsay.katz@mail.utoronto.ca]
  - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca]
abstract: "Public knowledge of what is said in parliament is a tenet of democracy, and a critical resource for political science research. In Australia, following the British tradition, the written record of what is said in parliament is known as Hansard. While the Australian Hansard has always been publicly available, it has been difficult to use for the purpose of large-scale macro and micro-level text analysis because it has only been available as PDFs or XMLs. Following the lead of the Linked Parliamentary Data project which achieved this for Canada, we provide a new, comprehensive, high-quality, rectangular, database that captures all proceedings of the Australian parliamentary debates from 1998 to the present using Hansard. The database is publicly available and can be linked to other datasets such as election results. The creation and accessibility of this database enables the exploration of questions that have not been possible to explore, serving as a valuable resource for both researchers and policymakers."
---

@@

The official written record of parliamentary debates, formally known as Hansard, plays a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions. Originating in the British parliament, the production of Hansard became tradition in many Commonwealth countries such as Canada, the United Kingdom, and Australia [@vice2017history]. Given the content and magnitude of these records, they have significance, particularly in the context of political science research. In the case of Canada, the Hansard has been digitized for 1901 to 2019 [@lipad]. Having a digitized version of Hansard enables researchers to perform advanced analyses on these records using text analysis tools and statistical modelling. Following the lead of that project, in this paper we introduce a novel database for the Australian Hansard. This is composed of individual datasets for each sitting day in the House of Representatives from 1998 to 2022, containing details on everything said in parliament in a form that can be readily used by researchers. With the development of tools for large-scale text analysis, this database will serve as a valuable resource for efficiently studying and exploring political behaviour in Australia over time.

The Australian House of Representatives performs a number of crucial governmental functions, such as creating new laws and overseeing government expenditure [@australia2018house, ch. 1]. The House operates under a parallel chamber setup, meaning there are two debate venues where proceedings take place: the Chamber, and the Federation Chamber. Sittings of the House follow a predefined order of business, regulated by procedural rules called standing orders [@australia2018house, ch. 8]. A typical sitting day in the Chamber has a number of scheduled proceedings including debates on government business, 90 second member statements, and Question Time [@australia2018house, ch. 8]. The Federation Chamber was created in 1994 as a subordinate debate venue of the Chamber. This allows for better time management of House business as its proceedings occur simultaneously with those of the Chamber [@australia2018house, ch. 21]. Sittings in the Federation Chamber are quite different to those of the Chamber in terms of their order of business and scope of discussion. Business matters discussed in the Federation Chamber are limited largely to intermediate stages of bill development, and the business of private Members [@australia2018house, ch. 21]. It is the recording and compilation of all of these proceedings on which Hansard is based, and it is essentially, but not entirely, verbatim.

A week or so after each sitting day, a transcript is available for download from the official Parliament of Australia website in both PDF and extensible markup language (XML) form. The PDF is the official release. For early decades there is a need to digitize PDFs using Optical Character Recognition (OCR) technology and there are many flaws [@sherratt]. The PDF imposes formatting designed for humans to read with ease, whereas XML is designed for consistency and machine legibility. The nature of XML enables us to more easily use code to manipulate these records at scale, motivating our choice to develop our database solely using the XML formatted files. In cases where we were unsure on how to proceed with processing the XML, we defer first to the PDF, and then to the video recording of the proceeding, if available.

At present, the Hansard format that is available on the Parliament of Australia website is not accessible for large scale analysis. To this point, various researchers have had to create their own databases of usable, complete data based on content from the Australian Parliament website. For instance, @sherratt created an online, easy to read database of Hansard from 1901 to 1980 using the XML files. These data can be navigated by year, parliament, people, and bills [@sherratt]. To make the Australian Parliamentary Handbook more accessible, @Leslie_2021_HoR_Aus has released an `R` package which includes data on all Members of the Australian House of Representatives from 1945 to 2019. Further, @auspol created the `AustralianPoliticians` `R` package, which contains several datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021.

Many papers exist which use components of Australian Hansard to explore various research topics. For example, @salisbury2011 used online Hansard records to investigate the occurrences of unparliamentary comments by members of the House, where the Speaker tells that member to withdraw their remark. @rasiah2010framework worked with Question Time data from Hansard transcripts during February and March of 2003, to investigate resistance of politicians in answering questions about Iraq. In their work, @fraussen2018 use Hansard to quantify political prominence by investigating strategic mentions of interest groups by elected officials. Finally, the work of @alexander2021 offers a dataset of the Australian Hansard, along with an analysis of the effect of elections and changes in Prime Ministers upon topics mentioned in parliament. @alexander2021 created this database with the static PDF versions of Hansard, using OCR to digitize these files into text which is suitable for analysis. This means there are considerable digitization errors especially in the first half of the dataset.

@@

> ```         
>      <hansard>
>        1. <session.header>
>        2. <chamber.xscript>
>           a)  <business.start>
>           b)  <debate>
>               i.  <debateinfo>
>               ii. <debate.text>
>               iii. <speech>
>               iv. <subdebate.1>
>                   (1) <subdebateinfo>
>                   (2) <subdebate.text>
>                   (3) <speech>
>                   (4) <subdebate.2>
>                       (a) <subdebateinfo>
>                       (b) <subdebate.text>
>                       (c) <speech>
>       3. <fedchamb.xscript>
>       4. <answers.to.questions>
>           a)  <question>
>           b)  <answer>
> ```

The outer-most node, also known as the parent node, is denoted `<hansard>` and serves as a container for the entire document. This parent node may have up to four child-nodes, where the first child-node contains details on the specific sitting day. Next, `<chamber.xscript>` contains all proceedings of the Chamber, `<fedchamb.xscript>` contains all proceedings of the Federation Chamber, and `<answers.to.questions>` contains Question Time proceedings. Note that the Federation Chamber does not meet on every sitting day, so this child element is not present in every XML file. The use of separate child nodes allows for the distinction of proceedings of the Chamber and Federation Chamber. The structure of the `<chamber.xscript>` and `<fedchamb.xscript>` nodes are generally the same, where the proceeding begins with a business start which is followed by a series of debates. Debate nodes can contain a `<subdebate.1>` child-node which has a `<subdebate.2>` child-node nested within it. That said, sometimes `<subdebate.2>` is not nested within `<subdebate.1>`. Each of these three elements (i.e. `<debate>`, `<subdebate.1>`, and `<subdebate.2>`) as well as their respective sub-elements contain important information on the topic of discussion, who is speaking, and what is being said. The `<speech>` node within each one contains the bulk of the text associated with that debate or sub-debate. A typical `<speech>` node begins with a `<talk.start>` sub-node, providing information on the speaker and the time of their first statement. Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate settings --- they are often composed of a series of interjections and continuations. These statements are categorized under different sub-nodes depending on their nature, such as `<interjection>` or `<continuation>`. The final key component of Hansard is Question Time, in which questions and answers are classified as unique elements. More detail on the purpose and processing of Question Time will follow in @sec-qa.

@@

![Snapshot of the beginning of the XML file for Hansard on 25 February 2020](images/xml1.png){#fig-xml1}

@@

The next step was to further develop our script to produce tidy data sets containing each parsed element, where each statement is separated onto its own row with details about the speaker, and rows are placed in chronological order. This first involved correcting the variable classes and adding serveral indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or sub-debate 1 versus sub-debate 2. The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed. In other words, any interjections, comments made by The Speaker or Deputy Speaker and continuations within an individual speech were all parsed together as a single string. As such, the name, name ID, electorate and party details were only provided for the person whose turn it was to speak. Splitting up these speeches in a way which would be generalizable across sitting days required much thought and effort. @sec-interject will provide further details on the intricacies of this task.

Since we are looking at a wide time span of documents, there are many changes in the way they are formatted over time. These became apparent as we ran our script on XML files from earlier sitting days. Some changes are as subtle as a differently named child-node, while others are as extensive as a completely different nesting structure. Smaller changes were accounted for as we became aware of them, and embedded into the code in a way that would not cause issues for parsing more current Hansards with subtle differences in formatting. However, as mentioned, more significant changes in the XML structure of Hansard are what necessitated the development of separate scripts as we worked backwards in time. Further, while working backward in time, it became clear that not every sitting day contains every possible XML element. For example, some days did not have sub-debate 2 content, and some days did not have a Federation Chamber proceeding. To improve the generalizability of these scripts, if-else statements were embedded within the code wherever an error might arise due to a missing element. For example, the entire Federation Chamber block of code is wrapped in an if-else statement for each script, so that it only executes if what the code attempts to parse exists in the file.

@@

While the modifications needed to develop the second script were quite straightforward, this was not the case for our next script. The typical tree structure of Hansard XMLs spanning from 1998 to March 2011 has an important difference from that of XMLs released after March 2011, necessitating many changes to be made in our methodology. In XMLs after March 2011, which our first two scripts successfully parse, the first two child-nodes of `<speech>` are typically `<talk.start>`, and `<talk.text>`. The first child-node contains data on the person whose turn it is to speak, and the second contains the entire contents of that speech --- including all interjections, comments, and continuations. After the `<talk.text>` element closes, there are typically a series of other child-nodes which provide a skeleton structure for how the speech proceedings went in chronological order. For example, if the speech began, was interrupted by one member, and then continued uninterrupted until the end, there would be one `<interjection>` node and one `<continuation>` node following the `<talk.text>` node. These would contain details on the person who made each statement such as their party and electorate.

@@

This was not isolated to just the beginning of speeches --- details on individuals interjecting or commenting during speeches were also captured this way. To separate statements out correctly, we collected all of these patterns using the `<talk.start>` node, and used them to split statements wherever one of these patterns was found. After separating the statements, we were able to remove these patterns from the body of text. We also used this method of extracting and later removing unwanted patterns for other pieces of data which did not belong to the debate proceedings, such as sub-debate titles.

Once we finalized this new method of processing the data, we proceeded with data cleaning using the same general approach as in the first two scripts to produce the same structure of CSV output. We then worked backwards in time and modified the code as needed for generalizability. Throughout this process we found many transcription errors present in the XMLs from earlier years. We fixed these manually, deferring to the official release to ensure the correct information was filled in. Since there were a number of transcription errors specific to the 2000s, we chose to create a fourth script for parsing 1998 and 1999. This allowed us to remove all the code which was needed to resolve specific transcription errors of the 2000s, to avoid an overly long script and in turn improving computational efficiency. As such, our fourth script is essentially the same as the third, with the only difference being that it has code specific to fixing transcription errors from 1998 and 1999.

@@

A key characteristic of the Australian parliamentary system is the ability for the executive government to be held accountable for their decisions. One core mechanism by which this is achieved is called Question Time. This is a period of each sitting day in the Chamber where members of the House can ask ministers two types of questions: questions in writing which are written in advance, or questions without notice which are asked verbally in the Chamber and are responded to in real time [@house2021]. Parsing the components of Question Time required a slightly different approach than that of the debate speech, because of its unique structure in the XML document. Questions without notice are included directly in the `"chamber.xscript"` child node, with sub-child nodes called `"question"` and `"answer"` to differentiate the two. Questions in writing, however, are embedded in their own child node called `"answers.to.questions"` at the end of the XML file.

To parse questions without notice and questions in writing in the first two scripts, we extracted all question and answer elements from the `"chamber.xscript"` and `"answers.to.questions"` child nodes. For the third and fourth scripts, our method of parsing the `"chamber.xscript"` speeches meant that all questions without notice content was already parsed in order. Like the rest of the speech content, we used those patterns of data preceding the text to separate questions and answers. Finally, since questions in writing exist in their own child node we were able to use the same parsing method for the third and fourth scripts as we did for the first and second scripts.

@@

As mentioned in @sec-diff, more recent years of Hansard XMLs contain a series of child-nodes which exist to capture the structure of interruptions in that speech. @fig-xml3 provides an example of this, where the speech was interrupted by a comment from The Deputy Speaker, and then the member continued their speech. Looking at the element names highlighted in blue, these child-nodes do not contain the actual text for the interjection or continuation --- this text is embedded within the speech above it. However, as shown by the content highlighted in pink in @fig-xml3, we were able to extract useful details on the individual interjecting which we could use later. Making use of this structure, we extracted names and information of all individuals that were categorized within the XML as interjections. We stored this as a dataframe called `"interject"`.[^1]

@@

We then created lists using both the `interject` and `main` dataframes to capture all the names of individuals who spoke that day. We added the names of all Members in a number of unique formats, due to the frequent variation in how names are transcribed in Hansard. When a Member interjects or continues a speech, the usual form of their name is a title followed by their first name or first initial and/or last name. There is also variation in the capitalization of these names.[^2] Another source of variation is in individuals with more than one first name, as sometimes only their initial first name is written, while other times their entire first name is written. Additionally, some surnames have punctuation, and some surnames have specific capitalization such as "McCormack", where even in full capitalization, the first "c" remains lower case. This variation demands careful consideration when writing regular expression patterns to search for in the text. In these lists we also accounted for any general interjection statements transcribed that were not attributed to an individual, such as "An opposition member interjecting-".

[^2]: Sometimes when someone's first name is included, only their last name is capitalized, while sometimes their full name is capitalized, or other times neither are capitalized.

Having these lists enabled us to extract the names of Members and their associated titles as they exist in the text, by searching for exact matches with regular expression patterns. We then used these extracted names to split all the speeches up, using regular expressions with lookarounds. A lookaround can be added to a regular expression pattern to enhance the specificity of matches. These were used to ensure that the text was not being split in the wrong places, such as places where Members were simply being named in the statement of another Member.

@@

We then added an order variable to the dataset based on row number, to keep track of the order in which everything was said. The next step was to fill the name, name ID, electorate and party variables with the correct data for each row. We also wanted to add the gender and unique identifier for each individual as found in the `AustralianPoliticians` package. To do so, we created a lookup table, which contained the unique incomplete form in which the name was transcribed, and the corresponding full name, name ID, electorate, party, gender, and unique ID for that individual. @fig-lookup provides an example of this. We used the main dataset from the `AustralianPoliticians` package in the creation of each lookup table [@auspol].

@@

Next, we merged our main dataframe with the lookup table to replace any incomplete names with their full names, and to fill in any gaps with available name ID, electorate, party, gender, and unique ID information. Finally, we were able to add a flag for interjections. Grouping our data by the speech number, we defined an interjection as a statement made by anyone who is not The Speaker, The Deputy Speaker, or the Member whose turn it was to speak. @fig-interject provides an example of a Federation Chamber proceeding with interjections. Evidently, statements made by the original speaker Stuart Robert or by The Deputy Speaker Maria Vamvakinou are not flagged as interjections.
